Replication on multicore considering hierarchy and characteristics of the network

### 2013-03-21 paper.tex
Added a simple graph and prioritiesed attributes for network model

The network model is defined by communication channels, which in turn
are defined by a set of attributes, i.e.\
\begin{itemize}
\item reliability (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): Ethernet is not reliable,
  multicore interconnect networks often are
\item synchronized clocks: sychronized clocks + bound on propagation
  time $\rightarrow$ \emph{synchronous network} model. \\Then:
  $\exists$ algorithm for synchronous networks $\rightarrow
  \exists$ algorithm for asynchronous
\item Security \& and failure detection (and the cost for that)
\end{itemize}

These are more about performance:
\begin{itemize}
\item ``breakdown'' of message send cost: Ethernet has dominating
  propagation time vs.\ dominating send and receive time on multicores
\item latency between each pair of nodes
\end{itemize}

@@

% Express as:
We express the model in a graph, where nodes are processors and edges
are (on-hop?) communication links.

>>>>

The network model is defined by communication channels, which in turn
are defined by a set of attributes (here sorted by priority):
\begin{itemize}
\item latency (quantitative) between each pair of nodes
\item ``breakdown'' (quantitative) of message send cost: Ethernet has
  dominating propagation time vs.\ dominating send and receive time on
  multicores
\item synchronized clocks: sychronized clocks + bound on propagation
  time $\rightarrow$ \emph{synchronous network} model. \\Then:
  $\exists$ algorithm for synchronous networks $\rightarrow
  \exists$ algorithm for asynchronous
\item reliability (loss, link failure, in-order delivery, phantoms,
  corruption, duplicated messages): Ethernet is not reliable,
  multicore interconnect networks often are
\item Security \& and failure detection (and the cost for that)
\end{itemize}

@@

% Express as:
We express the model in a graph, where nodes are processors and edges
are (on-hop?) communication links. The machines we consider for now
only have bi-directional communication links. Other machines (like the
SCC) have uni-directional links, which is why we model the graph with
directed graph.
